Delta Factor - A New Authorization Factor

### 2022-08-07 paper1.tex
-

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{ article}

\usepackage{graphicx}
\graphicspath{ {~/Desktop/FINALpix/} }

@@

%---------------------------------------------------------------------------------------------------------------------
\section{Abstract}
TBA (As per professor) %This is modus operandi bc as the paper evolves, the abstract changes invariably
\section{Introduction}
\setlength{\baselineskip}{1.5\baselineskip}
\indent

@@

%---------------------------------------------------------------------------------------------------------------------
\section{Design Principles}
MITM Phishing TOOLkitS:\\
PHOCA - by our SUNY - Stonybrook research group\\
Evilginx, Muraena, and Modlishka \\

@@

\noindent % frame 			3 = arch of MITM PIX (In professional typesetting, this is called a strut.)
% 		[  : )  pix ] 
% \usepackage{graphicx}  				Atop - as a preamble
% \graphicspath{ {~/Desktop/FINALpix/} } 		Atop - as a preamble 
\includegraphics[width=\textwidth]{/ARCH_TYP_MPTK.png}
Fig-1 Architecture of a MITM\\

@@

%--------------------------------------------------------------------------------------------------------------------
\section{Algorithm: \textit{implementation details}}
\noindent
Algorithm fundamentals:\\
Since most authentication methods can be mitigated by applying modern phishing toolkits,
they can be detected through \textit{network traffic}.
There are numerous methods to validate the user through various methods, but \textit{few \textbf{server} authentication methods}.
We propose reverse 2FA authentication method to \textbf{validate the server from the client perspective}.
We to want validate the link between the server plus client, by fingerprinting common \textbf{connection} details and independently verifying shared secrets.\\

@@

@@

\section{CITATIONS} % OUT-OF-ORDER intentional. Point number before "CITATIONS" auto-changed 
\noindent
Public Internet Standards (Various Authors)

@@

\noindent
https://datatracker.ietf.org/doc/html/rfc4086 - Making High Entropy Secrets

@@

\noindent
Reference implementations provided by papers + standardized code\\
TOTP - https://datatracker.ietf.org/doc/html/rfc6238
HOTP - https://datatracker.ietf.org/doc/html/rfc4226 
COTP - xxxxxxxxxxxxxxx TBA\\

>>>>

% New = "Delta Factor" due to line width
\documentclass[a4paper, 11pt]{article} 				%Short reports and scientific journals
% \documentclass{report}							% Books and thesis
\usepackage{graphicx}
\graphicspath{ {/Users/thomasperez/Desktop/finalpix/} }		%abs 
% \graphicspath{{../pdf/}{D:\ImagesforProjectLatex}}

@@

%---------------------------------------------------------------------------------------------------------------------
% Following exactly professor's Canvas example
\section{Abstract}
TBA (As per professor) %This is modus operandi bc as the paper evolves, the abstract changes invariably
\section{Introduction}
\setlength{\baselineskip}{1.5\baselineskip}
\indent

@@

%---------------------------------------------------------------------------------------------------------------------
% Still following exactly professor's Canvas example
\section{Design Principles}
MITM Phishing TOOLkitS:\\
PHOCA - by our SUNY - Stonybrook research group\\
Evilginx, Muraena, and Modlishka \\

@@

% frame 			3 = arch of MITM PIX (In professional typesetting, this is called a strut.)
% 		[  : )  pix ] 
  % \usepackage{graphicx}  					Atop - as a preamble
  % \graphicspath{ {~/Desktop/FINALpix/} } 		Atop - as a preamble 
\includegraphics[width=\textwidth]{pix1}
 %\includegraphics[\textwidth]{pix1}

Fig-1 Architecture of a MITM\\

@@

%--------------------------------------------------------------------------------------------------------------------
% Still following exactly professor's Canvas example
\section{Algorithm: \textit{implementation details}}
\noindent
Algorithm fundamentals:\\
Since most authentication methods can be mitigated by applying modern phishing toolkits,
they can be detected through \textit{network traffic}.
There are numerous methods to validate the user through various methods, but \textit{few \textbf{server} authentication methods}.
We propose reverse 2FA authentication method to \textbf{validate the server from the client perspective}.
We to want validate the link between the server plus client, by fingerprinting common \textbf{connection} details and independently verifying shared secrets.\\

@@

\noindent
Code type "pseudocode" (because of simplicity):\\
code\\
code\\

%--------------------------------------------------------------------------------------------------------------------
\section{Experiment}				% Still following exactly professor's Canvas example
\noindent
Setup:\\
setup\\

\noindent
Details:\\
details\\

\noindent
Results:\\
results\\
figures and observations\\
analysis of the results\\

@@

\section{CITATIONS - Chicago style} % OUT-OF-ORDER intentional. Point number before "CITATIONS" auto-changed 
\noindent
Public Internet Standards (Various Authors)

@@

\noindent
https://datatracker.ietf.org/doc/html/rfc4086 - High Entropy Secrets

@@

\noindent
Reference implementations provided by papers + standardized code\\
TOTP - https://datatracker.ietf.org/doc/html/rfc6238\\
HOTP - https://datatracker.ietf.org/doc/html/rfc4226 \\
COTP - (\textbf{citation TBA})\\
